Entrainment of low Mach number thermals in stratified domains

### 2019-05-29 tex/stratified_thermals.tex
Abstract.

\begin{abstract}
``Entropy rain,'' or the downard propagation of low entropy fluid, has been hypothesized as a dominant mechanism for carrying the solar luminosity in light of the recent Solar Convective Conundrum.
One possible dynamical manifestation of these ``raindrops'' is that of dense, propagating vortex rings, referred to as ``thermals'' in the context of Earth's atmosphere.
In this work, we develop an analytical theory describing entrainment in dense, antibuoyant vortex rings in stratified atmospheres.
We show that this theory describes the evolution of laminar, axisymmetric thermals in highly stratified atmospheres and into the boussinesq limit.
We discuss what the evolution of these thermals implies for the entropy rain hypothesis.
\end{abstract}

>>>>

\begin{abstract}
% first sentence should state the solar convective conundrum. Something like: Historically, the sun's luminosity was thought to be carried by large-scale convective flows, but recent observations show no such flow exists.
% second paragraph should introduce entropy rain, e.g.: In place of large-scale flows, some have suggested the solar luminosity may be transported by small ``droplets'' of rapidly falling, low entropy fluid
This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant ``thermals'' in the Earth's atmosphere.
In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
We discuss what the evolution of these thermals implies for the entropy rain hypothesis. % should replace this with a summary of the implications
\end{abstract}
